Characterization of gaps in directly bonded Si compound optics

### 2014-10-22 AO_bondedSi.tex
closes #21- cut Fig 8, which was photo of IR bubble and fringes

We looked for the indication of large gaps detectable as ``IR bubbles'' \cite{1992JEMat..21..669M} with IR imaging.  The detector was an IR Vista $\alpha$NIR infrared focal plane array, with 312 $\times$ 252 pixels, with 30 $\mu$m square pixels.  We used a 50 mm F/2 lens, with a fiber optic white light illumination source.  We estimate that the lamp-detector combination was sensitive to wavelengths in the range 1.1-1.6 $\mu$m.  The field of view sub-sampled the 4 inch diameter wafers, so we dithered the sample.  No effort was made to flat field the detector, so copious detector non-uniformities and vignetting are present in our images.  It was easy to detect IR bubbles despite the detector artifacts since the bubbles translate with the wafer during dithering.  We detected IR bubbles in all 3 of the bonded Si pucks on which we recorded IR images.  The bubble areal density varied from about 4 per 100 mm diameter bonded wafer pair to over 20 per bonded wafer pair.  Naturally, the unbonded DSP wafers show no such IR bubbles, which are entirely attributable to the gaps between bonded substrates as discussed in the literature (see Section \ref{secHistory}).  Figure \ref{IRbubble} shows an example of one of the IR bubbles in which several bright and dark fringes are clearly discernible.  No attempt at quantitative measurement was made on the IR images due to evidence that the detector is non-linear.  The morphology was clear regardless of the detector response.

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/IR_bubble.pdf}}
\caption{Photo of part VG09 with transmission image of a bubble highlighted\label{IRbubble}.  The right side photo shows the 75 mm diameter wafer with blue Sharpie rectangles indicating the position of different spectral measurements (as detailed in the next section).  The yellow circle in the photo highlights the outline of the location of an IR bubble we detected.  The bubble shows $\sim2$ fringes over the effective wavelength range 1.1-1.6 $\mu$m.  This fringe pattern is consistent with a gap comparable to this measurement wavelength.  The pointlike measurement artifacts, Sharpie marker, and vignetting are perceptible in the raw IR image.  Our interpretation of the IR bubbles is robust against these artifacts.  The area surrounding the IR bubble appears to be mostly devoid of large (wavelength-scale) gaps, since the transmission is fairly uniform, and consistent with the brightest fringe of the IR bubble.  }
\end{figure}

>>>>

We looked for the indication of large gaps detectable as ``IR bubbles'' \cite{1992JEMat..21..669M} with IR imaging.  The detector was an IR Vista $\alpha$NIR infrared focal plane array, with 312 $\times$ 252 pixels, with 30 $\mu$m square pixels.  We used a 50 mm F/2 lens, with a fiber optic white light illumination source.  We estimate that the lamp-detector combination was sensitive to wavelengths in the range 1.1-1.6 $\mu$m.  The field of view sub-sampled the 4 inch diameter wafers, so we dithered the sample.  No effort was made to flat field the detector, so copious detector non-uniformities and vignetting are present in our images.  It was easy to detect IR bubbles despite the detector artifacts since the bubbles translate with the wafer during dithering.  We detected IR bubbles in all 3 of the bonded Si pucks on which we recorded IR images.  The bubble areal density varied from about 4 per 100 mm diameter bonded wafer pair to over 20 per bonded wafer pair.  Naturally, the unbonded DSP wafers show no such IR bubbles, which are entirely attributable to the gaps between bonded substrates as discussed in the literature (see Section \ref{secHistory}).  No attempt at quantitative measurement was made on the IR images due to evidence that the detector is non-linear.  The morphology was clear regardless of the detector response.
